Correlation of filter methods

### 2019-06-28 analysis/filter-correlation.Rmd
wflow_publish(knitr_in("analysis/filter-correlation.Rmd"), view = FALSE)
export filter-correlation images

```{r eda-20, warning=FALSE}
# combine filter values

@@

```{r}
# recode levels so that they are unique
fv_all_list = map2(list(fv_vi_info.gain5$data, fv_vi_info.gain10$data,
  fv_vi_info.gain15$data, fv_vi_info.gain20$data,
  fv_vi_info.gain25$data, fv_vi_info.gain30$data),
  list(5, 10, 15, 20, 25, 30), ~
    dplyr::mutate(.x, method = recode(.x$method, FSelectorRcpp_information.gain = glue("FSelectorRcpp_information.gain-{.y}"))))

@@

```{r eda-21}
# combine filter values

@@

```{r eda-22}
# combine filter values

@@

>>>>

```{r correlation-filter-vi, warning=FALSE, dev = c("png", "pdf")}
# combine filter values

@@

```{r correlation-nbins, warning=FALSE, dev = c("png", "pdf")}
# recode levels so that they are unique
fv_all_list = map2(list(fv_vi_info.gain5$data, fv_vi_info.gain10$data,
  fv_vi_info.gain15$data, fv_vi_info.gain20$data,
  fv_vi_info.gain25$data, fv_vi_info.gain30$data),
  list(5, 10, 15, 20, 25, 30), ~
    dplyr::mutate(.x, method = recode(.x$method, FSelectorRcpp_information.gain = glue("FSelectorRcpp_information.gain-{.y}"))))

@@

```{r filter-correlation-3, warning=FALSE}
# combine filter values

@@

```{r filter-correlation-4, warning=FALSE}
# combine filter values

@@

```{r filter-correlation-5, echo = FALSE}
file_move("docs/figure/filter-correlation.Rmd/correlation-nbins-1.pdf",
          "code/98-paper/journal/")
file_move("docs/figure/filter-correlation.Rmd/correlation-filter-vi-1.pdf",
          "code/98-paper/journal/")
```
